---
title: "p8105_hw1_zk2275"
author: "Zhuodiao Kuang"
date: "2023-9-16"
output: github_document
---

# Problem 1

## Load the library and dataset

```{r}
library(moderndive)
library(ggplot2)
data("early_january_weather")
```

## Short description using inline R code

* The dataset has 15 variables, including `r names(early_january_weather)`. Besides, it records temperatures and pressures, and other characters in `r length(early_january_weather$origin)` different origins, from `r min(early_january_weather$time_hour)` to `r max(early_january_weather$time_hour)`.

* This dataset has `r nrow(early_january_weather)` row and `r ncol(early_january_weather)` columns.

* The mean temperature is `r mean(early_january_weather$temp)`.

## Make a plot and export it to my project directory

```{r}
ggplot(early_january_weather, aes(x=time_hour, y = temp, color = humid)) + geom_point()

ggsave("scatter_plot.pdf", height = 4, width = 6)
```

In the two weeks recorded by the data, the temperature showed a cyclical change every day, and the overall trend was rising. The humidity is generally rising with the temperature.


