---
title: "p8105_hw1_zk2275"
author: "Zhuodiao Kuang"
date: "2023-9-16"
output: github_document
---

# Problem 1

## Load the library and dataset

```{r}
library(moderndive)
library(ggplot2)
library(tidyverse)
data("early_january_weather")
```

## Short description using inline R code

* The dataset has 15 variables, including `r names(early_january_weather)`. Besides, it records temperatures and pressures, and other characters in `r length(early_january_weather$origin)` different origins, from `r min(early_january_weather$time_hour)` to `r max(early_january_weather$time_hour)`.

* This dataset has `r nrow(early_january_weather)` row and `r ncol(early_january_weather)` columns.

* The mean temperature is `r mean(early_january_weather$temp)`.

## Make a plot and export it to my project directory

```{r}
ggplot(early_january_weather, aes(x=time_hour, y = temp, color = humid)) + geom_point()

ggsave("scatter_plot.pdf", height = 4, width = 6)
```

In the two weeks recorded by the data, the temperature showed a cyclical change every day, and the overall trend was rising. The humidity is generally rising with the temperature.

# Problem 2

## Create a data frame

```{r}
data2 =
  tibble(
    vec_num = rnorm(10, sd = 1, mean = 1),
    vec_logic = vec_num > 0,
    vec_char = character(10),
    vec_level = factor(rep(1:3, length.out = 10), levels = c("low", "median" , "high"))

         )
data2
```


## Try the pull function to calculate the mean of each variable

```{r}
num <- data2 %>% pull(vec_num)
mean(num)
logic <- data2 %>% pull(vec_logic)
mean(logic)
char <- data2 %>% pull(vec_char)
mean(char)
fac<- data2 %>% pull(vec_level)
mean(fac)
```

* The sample of size 10 and the logical vector can work, but the character vector and the factor vector don't work.

## Convert variables

```{r ,eval=FALSE}
logic_2_num <- as.numeric(logic)
char_2_num <- as.numeric(char)
fac_2_num <- as.numeric(fac)
logic_2_num
char_2_num
fac_2_num
```

*  The values of the logical variable are one or zero, which stands or 'true' and 'false'.

*  The values of the character variable are NAs, because the original values are NAs. But if original values are not null, the converted ones are still null, which could not be recognized as numbers.

*  The values of the factor variable are all null.

## But it does help explain what happens when I try to take the mean.

We can only take the mean when the variables are or can be converted to numbers!


